---
title: "Transfer Function Modeling with R"
author: "Finn Vaughankraska"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_md: true
---

```{r setup, include=FALSE}
# libraries
library(knitr)
library(forecast)  # For ARIMA and forecasting
library(ggplot2)   # For plotting
library(dplyr)     # For data manipulation

set.seed(123)
```

# Introduction
In this report, we will demonstrate how to implement a transfer function model in R using the forecast package. Transfer functions model the relationship between an output time series and one or more input time series, accounting for potential lags and other dynamics...

# Exploratory Analysis
llorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.orem ipsum.
```{r qplot, fig.width=4, fig.height=3, message=FALSE}
summary(cars)
qplot(speed, dist, data=cars) + geom_smooth()
```
lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.lorem ipsum.

# Baseline Model

# Model Implementing Transfer Functions

# Results and Comparisons
Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. 

Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. 

Here are some key results that might be very insightful. Here are some key results that might be very insightful. Here are some key results that might be very insightful. 

# Conclusion
lorem ipsum